---
title: "Final_project"
author: "Natashia Nygaard"
date: "19/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load Libraries and mapbox api

```{r mapbox, eval=FALSE, echo=TRUE}
my_token <- "pk.eyJ1IjoibWFwbmF0IiwiYSI6ImNrenk3eGx3aDAybmgydm1saTY5bXZlcjYifQ.V552lWpfCPz_i34FvQ5uBg"

library(mapboxapi)
mb_access_token(my_token, install = TRUE)
```
```{r libraries, eval=FALSE, echo=TRUE}
library(sf)
library(raster)
library(tidyverse)
library(leaflet)

install.packages('leaflet.extras')
library(leaflet.extras)
library(htmlwidgets)
library(RColorBrewer)

```

```{r more libraries, eval=FALSE, echo=TRUE}
library(jsonlite)
library(tidytext)
library(dplyr)
library(Rcpp)
library(fasterize)
library(opencage)
```


```{r opencage, eval=FALSE, echo=TRUE}
Sys.setenv(OPENCAGE_KEY = "db5bcbbaa16443448c218247dca5d6ec")
```

# Define and save universities as spatial elements

## Define and save the current universities 

```{r current university locations, eval=FALSE, echo=TRUE}
Current_universities <- c("København","Aarhus","Odense","Aalborg","Lyngby","Frederiksberg","Roskilde","Herning","Emdrup","Esbjerg","Kolding","Slagelse","Sønderborg","Esbjerg","Ballerup")
```


## Use the oc_forward function to find the coordinates of the current universities, based on the names of the cities 

```{r current universities map, eval=FALSE, echo=TRUE}
c_u <- oc_forward_df(placename = Current_universities, countrycode = "DK", limit =1, no_annotations = TRUE)


```

## Define and save the future universities 

```{r future university locations, eval=FALSE, echo=TRUE}
Future_universities <- c("Esbjerg","Foulum","Herning","Hirtshals","Hjørring","Holbæk","Kalundborg","Kolding","Køge","Nykøbing Falster","Næstved","Risø","Rødby","Rønne","Skive","Slagelse","Struer","Sønderborg","Vejle")
```


## Use the oc_forward function to find the coordinates of the future universities, based on the names of the cities 

```{r future universities map, eval=FALSE, echo=TRUE}
f_u <- oc_forward_df(placename = Future_universities, countrycode = "DK", limit =1, no_annotations = TRUE)


```


## Use the st_as_sf to convert the universities to sf object 

```{r converting to sf objects, eval=FALSE, echo=TRUE}
#Convert to sf object

c_u_sf <- st_as_sf(c_u, coords = c("oc_lng", "oc_lat"), crs = 4326)
f_u_sf <- st_as_sf(f_u, coords = c("oc_lng", "oc_lat"), crs = 4326)


```

## Creating a cycling range isochrone based on the current universities, defining the range to be 20 minutes 
```{r cycliing range current universities, eval=FALSE, echo=TRUE}
cycling_isos_cu <- mb_isochrone(
  c_u_sf,
  profile = "cycling",
  time = 20,
  id = "placename"
)
```

## Using mapbox to create a map of this cycling isochrone ranging around the current universities 
```{r cycling range future universities mapped, eval=FALSE, echo=TRUE}
library(mapboxapi)

mapbox_map_cu <- leaflet() %>%
  addMapboxTiles(style_id = "streets-v11",
                 username = "mapbox") 

mapbox_map_cu %>%
  addPolygons(data = cycling_isos_cu,
              popup = ~id)


```

## Creating a cycling range isochrone based on the future universities, defining the range to be 20 minutes 

```{r cycling isochrone future universities, eval=FALSE, echo=TRUE}
cycling_isos_fu <- mb_isochrone(
  f_u_sf,
  profile = "cycling",
  time = 20,
  id = "placename"
)
```

## Using mapbox to create a map of this cycling isochrone ranging around the future universities 

```{r add cycling map future universities, eval=FALSE, echo=TRUE}

library(mapboxapi)

mapbox_map_fu <- leaflet() %>%
  addMapboxTiles(style_id = "streets-v11",
                 username = "mapbox") 

mapbox_map_fu %>%
  addPolygons(data = cycling_isos_fu,
              popup = ~id)



```
## Read the data of the young people's geographical location, using st_read 
```{r young people data, eval=FALSE, echo=TRUE}
young_people <- st_read("../in/unge_demografi.csv", options = "", stringsAsFactors = FALSE, header = FALSE)
```

## I have to change the column containing number of young people into numeric in order for later work
```{r numeric values, eval=FALSE, echo=TRUE}
young_numeric <- young_people$`19-22_years_old` %>% as.integer(young_people$`19-22_years_old`) 


```

## Turning the numeric values into a dataframe and changing the column name
```{r numeric to df, eval=FALSE, echo=TRUE}
library (plyr)
df <- ldply (young_numeric, data.frame)


names(df) <- c("19-22_years_old")


```

## Renaming the columns in the young_people dataframe
```{r rename columns, eval=FALSE, echo=TRUE}
names(young_people) <- c("municipality","19_years_old", "20_years_old","21_years_old","22_years_old","19-22_years_old")
```

## Using oc_forward_df in order to create spatial coordinates for the municipalities in the dataframe.
```{r get coordinates, eval=FALSE, echo=TRUE}
young_demo <- oc_forward_df(placename = young_people$municipality, countrycode = "DK", limit =1, no_annotations = TRUE)
```

## using st_as_sf to create create a sf object from the young_demo
```{r create sf object, eval=FALSE, echo=TRUE}
young_demo_sf <- st_as_sf(young_demo, coords = c("oc_lng", "oc_lat"), crs = 4326)
```

## Rename the columns
```{r rename columns again, eval=FALSE, echo=TRUE}
names(young_demo) <- c("municipality","lat", "long","placename")
```

## Join the young_people and young_demo by municipality to merge the number of young people in each municipality including the lat long 

```{r join dataframes, eval=FALSE, echo=TRUE}
young_people_demo <- young_people %>% inner_join(young_demo, by = "municipality")
```

## Merging the df containing numeric values and the young people demo df

```{r merged df, eval=FALSE, echo=TRUE}
young_df<- merge(df, young_people_demo)
```

## creating a clean dataframe, containing only the number of residents in the selected group of age for each municipality and the latitude and longitude for the municipalities.


```{r clean df, eval=FALSE, echo=TRUE}
clean_young_demo <- young_df %>% 
  select(c("lat","long", "19-22_years_old", "municipality"))
```




## find the five cities with most young people living there - the order in the df is descending, so the top 5 can be found using the tail function. 
```{r top 5 cities, eval=FALSE, echo=TRUE}
top_5 <- tail(clean_young_demo,n=5)

top_5


```
## Plot the five cities with most young people on the map containing the cycling isochrones with a distance range of 20 minutes, to see if any of them overlap 
```{r create and save future universities map, eval=FALSE, echo=TRUE}
#Define the title of the map of the future universities combined with the cycling range isos
title_fu <- "20 minute cycling range from future universities (blue) and top five cities with most young residents (red)"

# Create, save and plot the map 
top_5_cities_fu <- mapbox_map_fu %>%
  addPolygons(data = cycling_isos_fu,
              popup = ~id) %>%
  addCircleMarkers(lng=top_5$long, lat=top_5$lat, color = "RED") %>%
  addControl(title_fu, position = "bottomleft") %>%
  addMiniMap(
    width = 100,
    height = 100,
    position = "topright")

saveWidget(top_5_cities_fu,"../out/top_5_cities_fu.html", selfcontained=TRUE)

top_5_cities_fu
```
## Plot the five cities with most young people on the map containing the cycling isochrones with a distance range of 20 minutes, to see if any of them overlap 
```{r create and save current universities map, eval=FALSE, echo=TRUE}
#Define title for the map of current universities and the cycling range isos
title_cu <- "20 minute cycling range from current universities (blue) and top five cities with most young residents (red)"

#Create, save and plot the map 
top_5_cities_cu <- mapbox_map_cu %>%
  addPolygons(data = cycling_isos_cu,
              popup = ~id) %>%
  addCircleMarkers(lng=top_5$long, lat=top_5$lat, color = "RED") %>%
  addControl(title_cu, position = "bottomleft") %>%
  addMiniMap(
    width = 100,
    height = 100,
    position = "topright")

saveWidget(top_5_cities_cu,"../out/top_5_cities_cu.html", selfcontained=TRUE)

top_5_cities_cu
```

